---
title: "Evaluating temperature-dependence of growth allometry"
author: "Max Lindmark, Jan Ohlberger, Anna Gårdmark"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
  df_print: paged
pdf_document: default
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE, cache=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 12,
  fig.asp = 0.618,
  fig.align ='center'
)
```

# Intro
Fit log-linear models to growth in line with MTE but with random effects, mass-temperature interactions and within species data.

```{r lib, message=FALSE}
# Load libraries, install if needed
library(tidyverse)
library(brms)
library(RCurl)
library(tidybayes)
library(bayesplot)
library(RColorBrewer)
library(viridis)
library(tidylog)
library(modelr)
library(patchwork)
library(sjPlot)
library(sjmisc)
library(sjlabelled)

options(mc.cores = parallel::detectCores()) 

# To load entire cache in interactive r session, do: 
# qwraps2::lazyload_cache_dir(path = "R/allometric_growth_model_cache/html")
```

## Read and explore data
* decide what to do with data beyond peak for a size group...

```{r read and exlplore data, warning=FALSE, message=FALSE}
# Read in your data file
dat <- 
  read.csv(text = getURL("https://raw.githubusercontent.com/maxlindmark/scaling/master/data/growth_analysis.csv"))

dat <- dat %>%
  group_by(species_ab) %>%
  filter(y > 0) %>% 
  mutate(log_y = log(y),
         log_mass_intra = log_mass - mean(log_mass),
         temp_arr_intra = temp_arr - mean(temp_arr)) %>% 
  ungroup()

dat <- dat %>%
  filter(y > 0) %>% 
  mutate(log_y = log(y),
         log_mass_ct = log_mass - mean(log_mass),
         temp_arr_ct = temp_arr - mean(temp_arr)) %>% 
  ungroup()


# Filter data points at below optimum temperatures
#dat <- dat %>% filter(above_peak_temp == "N")
colnames(dat)

ggplot(dat, aes(temp_c, mass_g*y, color = factor(mass_g))) + 
  geom_point() +
  facet_wrap(~species_ab, scales = "free") +
  theme_classic() +
  stat_smooth(se = FALSE) + 
  guides(color = FALSE) + 
  scale_color_viridis(discrete = TRUE)

ggplot(dat, aes(temp_c, y, group = factor(mass_g))) + 
  facet_wrap(~species_ab, scales = "free") +
  theme_classic() +
  stat_smooth(se = FALSE, color = "gray") + 
  geom_point(data = dat, aes(temp_c, y, color = above_peak_temp))

ggplot(dat, aes(temp_arr, log_y, group = factor(mass_g))) + 
  facet_wrap(~species_ab, scales = "free", ncol = 3) +
  theme_classic() +
  stat_smooth(method = "lm", se = FALSE, color = "gray") + 
  geom_point(data = dat, aes(temp_arr, log_y, color = above_peak_temp))

# No only using sub-optimum temperatures
ggplot(filter(dat, above_peak_temp == "N"), aes(temp_arr, log_y, group = factor(mass_g))) + 
  facet_wrap(~species_ab, scales = "free", ncol = 3) +
  theme_classic() +
  stat_smooth(method = "lm", se = FALSE, color = "gray") + 
  geom_point(data = filter(dat, above_peak_temp == "N"),
             aes(temp_arr, log_y, color = above_peak_temp))
```

## Fit models

```{r fit models, cache=TRUE, message=FALSE}
m_gauss <- brm(
  log_y ~ log_mass_ct*temp_arr_ct + (1 | species_ab),
  data = filter(dat, above_peak_temp == "N"),
  family = gaussian(), save_pars = save_pars(all = TRUE),
  control = list(adapt_delta = 0.95, max_treedepth = 12),
  iter = 4000, cores = 4, chains = 4)

prior_summary(m_gauss)

m_student <- brm(
  log_y ~ log_mass_ct*temp_arr_ct + (1 | species_ab),
  data = filter(dat, above_peak_temp == "N"),
  family = student(), save_pars = save_pars(all = TRUE),
  control = list(adapt_delta = 0.95, max_treedepth = 12),
  iter = 4000, cores = 4, chains = 4)

m_skew <- brm(
  log_y ~ log_mass_ct*temp_arr_ct + (1 | species_ab),
  data = filter(dat, above_peak_temp == "N"),
  family = skew_normal(), save_pars = save_pars(all = TRUE),
  control = list(adapt_delta = 0.95, max_treedepth = 12),
  iter = 4000, cores = 4, chains = 4)

loo_gauss <- loo(m_gauss, moment_match = TRUE)
loo_student <- loo(m_student, moment_match = TRUE)
loo_skew <- loo(m_skew, moment_match = TRUE)

loo_compare(loo_gauss, loo_student, loo_skew)
```

## Make plots for effect size

```{r plot, message=FALSE}
# First, what is the effect size?
b <- -0.37

df <- data.frame(
  temp_arr_ct = seq(min(dat$temp_arr_ct), max(dat$temp_arr_ct), length.out = 20)) %>% 
  mutate(temp_arr = round(temp_arr_ct + mean(dat$temp_arr), 1)) %>% 
  mutate(temp_c = round(1/(temp_arr * (8.617*10^-5)) - 273.15, 0))

df$b <- -0.37

df$b_temp <- -0.37 + 0.02*df$temp_arr_ct
summary(lm(b_temp ~ temp_c, data = df))
summary(lm(b_temp ~ temp_arr_ct, data = df))

ggplot(df, aes(temp_c, b_temp)) + geom_line() + geom_point() + 
  geom_point(data = df, aes(temp_c, b), color = "red")

# Summary
# https://cran.r-project.org/web/packages/sjPlot/vignettes/tab_model_estimates.html
tab_model(m_skew)

summary(m_skew)

# Compare with and without interaction
df_comp <- data.frame(expand.grid(
  mass = seq(0, 1000, 1),
  temp_arr_ct = seq(min(dat$temp_arr_ct),
                    max(dat$temp_arr_ct),
                    length.out = 20))) %>% 
  mutate(temp_arr = temp_arr_ct + mean(dat$temp_arr),
         temp_c = 1/(temp_arr * (8.617*10^-5)) - 273.15,
         log_mass = log(mass),
         log_mass_ct = log_mass + mean(dat$log_mass),
         temp_c_r = round(temp_c, digits = 0))

df_comp <- df_comp %>% 
  mutate(log_growth = 0.63 + log_mass_ct*-0.37 + temp_arr_ct*-0.61 + log_mass_ct*temp_arr_ct*0.02,
         log_growth_no_inter = 0.63 + log_mass_ct*-0.37 + temp_arr_ct*-0.61)

unique(df_comp$temp_c_r)
unique(df_comp$mass)

# Plot difference
df_comp %>% 
  filter(temp_c_r %in% c(15, 25) & mass > 0) %>% 
  pivot_longer(c(log_growth, log_growth_no_inter)) %>% 
  ggplot(aes(log_mass, value, name = name, color = factor(temp_c_r))) +
  geom_line()

pp <- df_comp %>% 
  filter(temp_c_r %in% c(15, 25) & mass > 10 & mass < 700) %>% 
  pivot_longer(c(log_growth, log_growth_no_inter)) %>% 
  ggplot(aes(mass, exp(value), linetype = name, color = factor(temp_c_r))) +
  facet_wrap(~temp_c_r, scales = "free", ncol = 1) +
  geom_line()

# Plot difference in %
unique(df_comp$mass)

pp2 <- df_comp %>% 
  filter(mass %in% c(10, 1000) & temp_c_r > 10 & temp_c_r < 25) %>% 
  mutate(log_growth_percent = 
           100 * ((log_growth - log_growth_no_inter) / log_growth_no_inter),
         log_growth_ratio = 
           (log_growth / log_growth_no_inter),
         growth_ratio = 
           (exp(log_growth) / exp(log_growth_no_inter))
         ) %>% 
  ggplot(aes(temp_c_r, growth_ratio, color = factor(mass))) +
  labs(y = "ratio: growth/(growth ignoring interaction)") +
  geom_line()

pp + pp2
```

## Plot model 

```{r plot model}
# Plot
conditional_effects(m_skew)

ggplot(dat, aes(temp_c, temp_arr)) +
  geom_point() +
  stat_smooth(method = "lm") + 
  geom_hline(yintercept = c(39, 41), color = "tomato") +
  geom_vline(xintercept = c(10, 24), color = "tomato")

pal <- brewer.pal(n = 3, name = "Set1")

summary(m_skew)

p1 <- data.frame(
  expand.grid(log_mass_ct = seq_range(dat$log_mass_ct, n = 101),
              temp_arr_ct = round(c(39, 41) - mean(dat$temp_arr), 1))) %>% 
  mutate(temp_arr = round(temp_arr_ct + mean(dat$temp_arr), 1)) %>% 
  mutate(temp_c = round(1/(temp_arr * (8.617*10^-5)) - 273.15, 0)) %>% 
  mutate(temp = paste(temp_arr, " (", temp_c, "°C)", sep = "")) %>% 
  add_predicted_draws(m_skew, re_formula = NA) %>%
  ggplot(., aes(x = log_mass_ct, y = .prediction,
                color = factor(temp), fill = factor(temp))) +
  stat_lineribbon(.width = c(.85, .95), alpha = 1/4) +
  stat_lineribbon(.width = 0, alpha = 0.7) +
  scale_color_brewer(palette = "Set1", name = "") +
  scale_fill_brewer(palette = "Set1", name = "Temperature") + 
  theme_classic(base_size = 10) +
  geom_point(data = dat, aes(log_mass_ct, log_y), inherit.aes = FALSE,
             size = 1.5, alpha = 0.6, shape = 21, color = "white", fill = "grey30") + 
  # guides(color = FALSE, fill = guide_legend(ncol = 1)) +
  guides(color = FALSE) +
  labs(x = "log(mass)") + 
  # annotate("text", 0, 4, size = 3, color = pal[2],
  #          label = "y=0.64 - 0.37×log(m) - 0.61×", fontface = "italic") + # Cold
  # annotate("text", 0, 3.5, size = 3, color = pal[1],
  #          label = "y=0.64 - 0.37×log(m) - 0.61×t", fontface = "italic") + # Warm
  theme(aspect.ratio = 1,
        legend.key.size = unit(0.5, "line"), 
        legend.text = element_text(size = 6),
        legend.title = element_text(size = 7),
        legend.spacing.x = unit(0.1, 'cm'),
        legend.margin = margin(0, 0, 0, 0),
        #legend.position = c(0.3, 0.2),
        legend.position = "bottom",
        plot.margin = unit(c(0, 0.1, 0, 0), "cm"))

p2 <- data.frame(
  expand.grid(log_mass_ct = round(c(2, 5) - mean(dat$log_mass), 2), # summary(dat$log_mass)
              temp_arr_ct = seq_range(dat$temp_arr_ct, n = 101))) %>% 
  mutate(log_mass = round(log_mass_ct + mean(dat$log_mass), 2)) %>% 
  add_predicted_draws(m_skew, re_formula = NA) %>%
  ggplot(., aes(x = temp_arr_ct, y = .prediction,
                color = factor(log_mass), fill = factor(log_mass))) +
  stat_lineribbon(.width = c(.85, .95), alpha = 1/4) +
  stat_lineribbon(.width = 0, alpha = 0.7) +
  scale_color_brewer(palette = "Dark2", name = "") +
  scale_fill_brewer(palette = "Dark2", name = "log(mass)") + # Check this! Not the centered scale
  theme_classic(base_size = 10) +
  geom_point(data = dat, aes(temp_arr_ct, log_y), inherit.aes = FALSE,
             size = 1.5, alpha = 0.6, shape = 21, color = "white", fill = "grey30") + 
  #guides(color = FALSE, fill = guide_legend(ncol = 1)) + 
  guides(color = FALSE) +
  labs(x = "Temperature (1/kT[K])") + 
  theme(aspect.ratio = 1,
        legend.key.size = unit(0.5, "line"), 
        legend.text = element_text(size = 6),
        legend.title = element_text(size = 7),
        legend.spacing.x = unit(0.1, 'cm'),
        legend.margin = margin(0, 0, 0, 0),
        #legend.position = c(0.2, 0.2),
        legend.position = "bottom",
        plot.margin = unit(c(0, 0, 0, 0), "cm"))

p3 <- m_skew %>%
  spread_draws(`b_log_mass_ct:temp_arr_ct`) %>%
  ggplot(aes(x = `b_log_mass_ct:temp_arr_ct`, fill = stat(x < 0))) +
  stat_halfeye(.width = c(0.85, 0.95)) + 
  theme_classic(base_size = 10) + 
  geom_vline(xintercept = 0, linetype = "dashed") +
  scale_fill_manual(values = c("gray90", "grey60")) +
  labs(x = "Mass×Temp. interaction") +
  #guides(fill = guide_legend(ncol = 1)) + 
  theme(aspect.ratio = 1,
        legend.key.size = unit(0.5, "line"), 
        legend.text = element_text(size = 6),
        legend.title = element_text(size = 7),
        legend.spacing.x = unit(0.1, 'cm'),
        legend.margin = margin(0, 0, 0, 0),
        #legend.position = c(0.8, 0.5),
        #legend.position = "bottom"
        legend.position = "bottom",
        plot.margin = unit(c(0, 0, 0, 0), "cm"))

(p1 | p2 | p3) + plot_annotation(tag_levels = "A")
ggsave("figures/Fig1.png", width = 6.5, height = 6.5, dpi = 600)

get_variables(m_skew)

p4 <- m_skew %>%
  spread_draws(b_Intercept, r_species_ab[species_ab, ]) %>%
  mutate(intercept_mean = b_Intercept + r_species_ab) %>%
  ggplot(aes(y = species_ab, x = intercept_mean)) +
  stat_halfeye() + 
  theme_classic(base_size = 12) + 
  #coord_cartesian(xlim = c(-0.2, 0.25)) + 
  scale_fill_manual(values = c("gray80", "tomato")) + 
  theme(legend.position = "bottom", 
        axis.text.y = element_text(face = "italic")) + 
  labs(y = "Species", x = "Intercept") +
  NULL

p4
ggsave("figures/Fig2.png", width = 3, height = 6, dpi = 600)
```

## Plot model diagnostics

```{r plot model validation}
# Model validation
posterior <- as.array(m_skew)
dimnames(posterior)

mcmc_trace(
  posterior, 
  pars = c("b_Intercept", "b_log_mass_ct", 
           "b_temp_arr_ct", "b_log_mass_ct:temp_arr_ct", "sd_species_ab__Intercept",
           "sd_species_ab__Intercept", "sigma", "alpha"),
  facet_args = list(ncol = 2, strip.position = "left")) + 
  geom_line(alpha = .2) +
  theme(text = element_text(size = 12),
        strip.text = element_text(size = 3),
        legend.position = c(0.6, 0.05),
        legend.direction = "horizontal") + 
  scale_color_viridis(discrete = TRUE, direction = -1) +
  theme_classic(base_size = 12) +
  theme(axis.text.x = element_text(angle = 90),
        #legend.position = "bottom",
        legend.position = c(0.75, 0.1),
        strip.text = element_text(size = 5),
        legend.direction = "horizontal") + 
  NULL

ggsave("figures/FigS1.png", width = 6.5, height = 6.5, dpi = 600)

# Posterior predictive
pp_check(m_skew) + 
  theme(text = element_text(size = 12),
        legend.position = c(0.15, 0.95),
        legend.background = element_rect(fill = NA)) + 
  scale_color_brewer(palette = "Dark2") +
  labs(color = "") +
  theme_classic(base_size = 14) +
  theme(legend.position = c(0.2, 0.9)) + 
  NULL

ggsave("figures/FigS2.png", width = 4, height = 4, dpi = 600)
```

## Continue here:
1. Sensitivity w r t temperature filter and species included. How certain are we about this scaling? First part of the paper is: is the math prediction supported in data? How large is the effect of ignore this scaling?

2. Where do species operate on their optimum curbe? See supporting figure in GCB. Can we do quantify average range to optimum on that data as well? Are species at the inflection point to the optimum temperature?

