---
title: "Evaluating temperature-dependence of growth allometry"
author: "Max Lindmark, Jan Ohlberger, Anna Gårdmark"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
  df_print: paged
pdf_document: default
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE, cache=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 12,
  fig.asp = 0.618,
  fig.align ='center'
)
```

# Intro
Fit log-linear models to growth in line with MTE but with random effects, mass-temperature interactions and within species data.

```{r lib, message=FALSE}
# Load libraries, install if needed
library(tidyverse)
library(brms)
library(RCurl)
library(tidybayes)
library(bayesplot)
library(RColorBrewer)
library(viridis)
library(tidylog)
library(modelr)
library(patchwork)

options(mc.cores = parallel::detectCores()) 

# To load entire cache in interactive r session, do: 
# qwraps2::lazyload_cache_dir(path = "R/allometric_growth_model_cache/html")
```

## Read and explore data
* decide what to do with data beyond peak for a size group...

```{r read and exlplore data, warning=FALSE, message=FALSE}
# Read in your data file
dat <- 
  read.csv(text = getURL("https://raw.githubusercontent.com/maxlindmark/scaling/master/data/growth_analysis.csv"))

dat <- dat %>%
  group_by(species_ab) %>%
  filter(y > 0) %>% 
  mutate(log_y = log(y),
         log_mass_intra = log_mass - mean(log_mass),
         temp_arr_intra = temp_arr - mean(temp_arr)) %>% 
  ungroup()

dat <- dat %>%
  filter(y > 0) %>% 
  mutate(log_y = log(y),
         log_mass_ct = log_mass - mean(log_mass),
         temp_arr_ct = temp_arr - mean(temp_arr)) %>% 
  ungroup()


# Filter data points at below optimum temperatures
#dat <- dat %>% filter(above_peak_temp == "N")
colnames(dat)

ggplot(dat, aes(temp_c, mass_g*y, color = factor(mass_g))) + 
  geom_point() +
  facet_wrap(~species_ab, scales = "free") +
  theme_classic() +
  stat_smooth(se = FALSE) + 
  guides(color = FALSE) + 
  scale_color_viridis(discrete = TRUE)

ggplot(dat, aes(temp_c, y, group = factor(mass_g))) + 
  facet_wrap(~species_ab, scales = "free") +
  theme_classic() +
  stat_smooth(se = FALSE, color = "gray") + 
  geom_point(data = dat, aes(temp_c, y, color = above_peak_temp))

ggplot(dat, aes(temp_arr, log_y, group = factor(mass_g))) + 
  facet_wrap(~species_ab, scales = "free", ncol = 3) +
  theme_classic() +
  stat_smooth(method = "lm", se = FALSE, color = "gray") + 
  geom_point(data = dat, aes(temp_arr, log_y, color = above_peak_temp))

# Now only using sub-optimum temperatures
ggplot(filter(dat, above_peak_temp == "N"), aes(temp_arr, log_y, group = factor(mass_g))) + 
  facet_wrap(~species_ab, scales = "free", ncol = 3) +
  theme_classic() +
  stat_smooth(method = "lm", se = FALSE, color = "gray") + 
  geom_point(data = filter(dat, above_peak_temp == "N"),
             aes(temp_arr, log_y, color = above_peak_temp))
```

## Fit models

```{r fit models, cache=TRUE, message=FALSE}
m_gauss <- brm(
  log_y ~ log_mass_ct*temp_arr_ct + (1 | species_ab),
  data = filter(dat, above_peak_temp == "N"),
  family = gaussian(),
  save_pars = save_pars(all = TRUE),
  #control = list(adapt_delta = 0.95, max_treedepth = 12),
  iter = 4000, cores = 4, chains = 4)

prior_summary(m_gauss)
pp_check(m_gauss)

m_student <- brm(
  log_y ~ log_mass_ct*temp_arr_ct + (1 | species_ab),
  data = filter(dat, above_peak_temp == "N"),
  family = student(),
  save_pars = save_pars(all = TRUE),
  control = list(adapt_delta = 0.95, max_treedepth = 12),
  iter = 4000, cores = 4, chains = 4)

pp_check(m_student)
summary(m_student)
plot(m_student)
conditional_effects(m_student)

m_skew <- brm(
  log_y ~ log_mass_ct*temp_arr_ct + (1 | species_ab),
  data = filter(dat, above_peak_temp == "N"),
  family = skew_normal(),
  save_pars = save_pars(all = TRUE),
  control = list(adapt_delta = 0.95, max_treedepth = 12),
  iter = 4000, cores = 4, chains = 4)

m_skew2 <- brm(
  log_y ~ log_mass_ct*temp_arr_ct + (1 + log_mass_ct| species_ab),
  data = filter(dat, above_peak_temp == "N"),
  family = skew_normal(),
  save_pars = save_pars(all = TRUE),
  control = list(adapt_delta = 0.99, max_treedepth = 12),
  iter = 4000, cores = 4, chains = 4)

m_stud2 <- brm(
  log_y ~ log_mass_ct*temp_arr_ct + (1 + log_mass_ct| species_ab),
  data = filter(dat, above_peak_temp == "N"),
  family = student(),
  save_pars = save_pars(all = TRUE),
  control = list(adapt_delta = 0.99, max_treedepth = 12),
  iter = 4000, cores = 4, chains = 4)

m_skew3 <- brm(
  log_y ~ log_mass_ct*temp_arr_ct + (1 + temp_arr_ct| species_ab),
  data = filter(dat, above_peak_temp == "N"),
  family = skew_normal(),
  save_pars = save_pars(all = TRUE),
  control = list(adapt_delta = 0.95, max_treedepth = 12),
  iter = 4000, cores = 4, chains = 4)

m_skew4 <- brm(
  log_y ~ log_mass_ct*temp_arr_ct + (1 + temp_arr_ct + log_mass_ct| species_ab),
  data = filter(dat, above_peak_temp == "N"),
  family = skew_normal(),
  save_pars = save_pars(all = TRUE),
  control = list(adapt_delta = 0.95, max_treedepth = 12),
  iter = 4000, cores = 4, chains = 4)

m_skew5 <- brm(
  log_y ~ log_mass_ct*temp_arr_ct + (1 + temp_arr_ct*log_mass_ct| species_ab),
  data = filter(dat, above_peak_temp == "N"),
  family = skew_normal(),
  save_pars = save_pars(all = TRUE),
  control = list(adapt_delta = 0.95, max_treedepth = 12),
  iter = 4000, cores = 4, chains = 4)

m_gauss5 <- brm(
  log_y ~ log_mass_ct*temp_arr_ct + (1 + temp_arr_ct+log_mass_ct| species_ab),
  data = filter(dat, above_peak_temp == "N"),
  family = gaussian(),
  save_pars = save_pars(all = TRUE),
  control = list(adapt_delta = 0.95, max_treedepth = 12),
  iter = 4000, cores = 4, chains = 4)

m_gauss6 <- brm(
  log_y ~ log_mass_ct*temp_arr_ct + (1 + temp_arr_ct*log_mass_ct| species_ab),
  data = filter(dat, above_peak_temp == "N"),
  family = gaussian(),
  save_pars = save_pars(all = TRUE),
  control = list(adapt_delta = 0.95, max_treedepth = 12),
  iter = 4000, cores = 4, chains = 4)


pp_check(m_skew)
print(summary(m_skew), digits = 4)
print(summary(m_skew2), digits = 4)
print(summary(m_stud2), digits = 4)

plot(m_skew)

plot(m_skew4)
plot(m_gauss6)
plot(m_stud2)
pp_check(m_gauss6)

ggplot(dat, aes(temp_arr_ct, log_y, color = species_ab)) + 
  geom_point() +
  stat_smooth(method = "lm", se = FALSE) + 
  stat_smooth(se = FALSE)

conditional_effects(m_skew)
print(summary(m_skew, prob = (1-0.074)), digits = 5)
print(summary(m_skew, prob = 0.85), digits = 5)
prior_summary(m_skew)

loo_gauss <- loo(m_gauss, moment_match = TRUE)
loo_student <- loo(m_student, moment_match = TRUE)
loo_student2 <- loo(m_stud2, moment_match = TRUE)
loo_skew <- loo(m_skew, moment_match = TRUE)
loo_skew2 <- loo(m_skew2, moment_match = TRUE, reloo = TRUE)
loo_skew3 <- loo(m_skew3, moment_match = TRUE)
#loo_skew4 <- loo(m_skew4, moment_match = TRUE)
#loo_skew5 <- loo(m_skew5, moment_match = TRUE)
loo_gauss5 <- loo(m_gauss5, moment_match = TRUE, reloo = TRUE)
loo_gauss6 <- loo(m_gauss6, moment_match = TRUE, reloo = TRUE)

loo_compare(loo_gauss, loo_student, loo_student2, loo_skew, loo_skew2, loo_skew3, loo_gauss5, loo_gauss6
            #, loo_skew4, loo_skew5, loo_gauss5
            )

plot(m_skew2)

pp_check(m_skew)
pp_check(m_skew5)
plot(m_skew5)
plot(m_gauss5)
plot(m_gauss)

# within species centering?
dat <- dat %>%
  group_by(species_ab) %>%
  mutate(log_mass_intra_ct = log_mass - mean(log_mass),
         temp_arr_intra_ct = temp_arr - mean(temp_arr)) %>%
  ungroup()

m_intra <- brm(
  log_y ~ log_mass_intra_ct*temp_arr_intra_ct + (1 + log_mass_intra_ct*temp_arr_intra_ct| species_ab),
  data = filter(dat, above_peak_temp == "N"),
  save_pars = save_pars(all = TRUE),
  control = list(adapt_delta = 0.95, max_treedepth = 12),
  iter = 4000, cores = 4, chains = 4)
 
plot(m_intra)

## non bayesian??
library(sdmTMB)
library(glmmTMB)

dat$species_ab <- as.factor(dat$species_ab)

m1 <- glmmTMB(formula = log_y ~ log_mass_ct*temp_arr_ct + (1|species_ab),
  data = filter(dat, above_peak_temp == "N"), REML = TRUE)

m2 <- glmmTMB(formula = log_y ~ log_mass_ct*temp_arr_ct + (1+log_mass_ct|species_ab),
  data = filter(dat, above_peak_temp == "N"), REML = TRUE)

m3 <- glmmTMB(formula = log_y ~ log_mass_ct*temp_arr_ct + (1+temp_arr_ct|species_ab),
  data = filter(dat, above_peak_temp == "N"), REML = TRUE)

# m4 <- glmmTMB(formula = log_y ~ log_mass_ct + temp_arr_ct + (1|species_ab),
#   data = filter(dat, above_peak_temp == "N"), REML = TRUE)
# 
# m5 <- glmmTMB(formula = log_y ~ log_mass_ct + temp_arr_ct + (1 + log_mass_ct|species_ab),
#   data = filter(dat, above_peak_temp == "N"), REML = TRUE)
# 
# m6 <- glmmTMB(formula = log_y ~ log_mass_ct + temp_arr_ct + (1 + temp_arr_ct|species_ab),
#   data = filter(dat, above_peak_temp == "N"), REML = TRUE)


AIC(m1, m2, m3)
#AIC(m1, m2, m3, m4, m5, m6)

# residuals?
d2 = dat %>% filter(above_peak_temp == "N")

library(DHARMa)
m2_sim_res <- simulateResiduals(m2)
m3_sim_res <- simulateResiduals(m3)

plot(m2_sim_res)
plot(m3_sim_res)

summary(m1)
summary(m2)
summary(m3)




df <- data.frame(var = "interaction",
                 upr = 0.02440 + c(1.96*0.01409),
                 lwr = 0.02440 - c(1.96*0.01409),
                 est = 0.02440)

ggplot(df, aes(var, y = est, ymin = lwr, ymax = upr)) +
  geom_point() + 
  geom_errorbar(width = 0) + 
  geom_hline(yintercept = 0, color = "red")

# plot(m_skew_intra)
# 
# m_skew_intra2 <- brm(
#   log_y ~ log_mass_intra_ct + log_mass_ct*temp_arr_ct + (1 + log_mass_ct*temp_arr_ct|species_ab),
#   data = filter(dat, above_peak_temp == "N"),
#   family = skew_normal(),
#   save_pars = save_pars(all = TRUE),
#   control = list(adapt_delta = 0.95, max_treedepth = 12),
#   iter = 4000, cores = 4, chains = 4)
# 
# plot(m_skew_intra2)
# 
# get_variables(m_skew_intra2)
# 
# m_skew_intra2 %>%
#   spread_draws(b_log_mass_ct, r_species_ab[log_mass_ct,]) %>%
#   median_qi(condition_mean = b_log_mass_ct + r_species_ab, .width = c(.95, .66)) %>%
#   ggplot(aes(y = log_mass_ct, x = condition_mean, xmin = .lower, xmax = .upper)) +
#   geom_pointinterval()
# 
# 
# m_skew_intra2 %>%
#   spread_draws(`b_log_mass_ct:temp_arr_ct`, r_species_ab[`log_mass_ct:temp_arr_ct`,]) %>%
#   median_qi(condition_mean = `b_log_mass_ct:temp_arr_ct` + r_species_ab, .width = c(.95, .66)) %>%
#   ggplot(aes(y = `log_mass_ct:temp_arr_ct`, x = condition_mean, xmin = .lower, xmax = .upper)) +
#   geom_pointinterval()

```

# this will be hard. glmmTMB says m3 is best, but m2 is within 2 and has better diagnostics. if I add the random mass effect the interaction dissapears. it's just not a very robust result, and I do not now really how to deal with it. 

```{r}
library(equatiomatic)
library(lme4)

m <- lmer(log_y ~ log_mass_ct*temp_arr_ct + (1 | species_ab),
          data = filter(dat, above_peak_temp == "N"))

extract_eq(m, intercept = "beta")
```

$$
\begin{aligned}
  \operatorname{log\_y}_{i}  &\sim N \left(\mu, \sigma^2 \right) \\
    \mu &=\alpha_{j[i]} + \beta_{1}(\operatorname{\log\_mass\_ct}) + \beta_{2}(\operatorname{temp\_arr\_ct}) + \beta_{3}(\operatorname{\log\_mass\_ct} \times \operatorname{temp\_arr\_ct}) \\
    \alpha_{j}  &\sim N \left(\mu_{\alpha_{j}}, \sigma^2_{\alpha_{j}} \right)
    \text{, for species\_ab j = 1,} \dots \text{,J}
\end{aligned}
$$



## Make plots for effect size

```{r plot, message=FALSE}
# First, what is the effect size?
# b <- -0.37
# 
# df <- data.frame(
#   temp_arr_ct = seq(min(dat$temp_arr_ct), max(dat$temp_arr_ct), length.out = 20)) %>% 
#   mutate(temp_arr = round(temp_arr_ct + mean(dat$temp_arr), 1)) %>% 
#   mutate(temp_c = round(1/(temp_arr * (8.617*10^-5)) - 273.15, 0))
# 
# df$b <- -0.37
# 
# df$b_temp <- -0.37 + 0.02*df$temp_arr_ct
# summary(lm(b_temp ~ temp_c, data = df))
# summary(lm(b_temp ~ temp_arr_ct, data = df))
# 
# ggplot(df, aes(temp_c, b_temp)) + geom_line() + geom_point() + 
#   geom_point(data = df, aes(temp_c, b), color = "red")
```

## Plot model 

```{r plot model}
# Plot
#conditional_effects(m_skew)

ggplot(dat, aes(temp_c, temp_arr)) +
  geom_point() +
  stat_smooth(method = "lm") + 
  geom_hline(yintercept = c(39, 41), color = "tomato") +
  geom_vline(xintercept = c(10, 24), color = "tomato")

pal <- brewer.pal(n = 3, name = "Set1")

summary(m_skew)

p1 <- data.frame(
  expand.grid(log_mass_ct = seq_range(dat$log_mass_ct, n = 101),
              temp_arr_ct = round(c(39, 41) - mean(dat$temp_arr), 1))) %>% 
  mutate(temp_arr = round(temp_arr_ct + mean(dat$temp_arr), 1)) %>% 
  mutate(temp_c = round(1/(temp_arr * (8.617*10^-5)) - 273.15, 0)) %>% 
  mutate(temp = paste(temp_arr, " (", temp_c, "°C)", sep = "")) %>% 
  add_predicted_draws(m_skew, re_formula = NA) %>%
  ggplot(., aes(x = log_mass_ct, y = .prediction,
                color = factor(temp), fill = factor(temp))) +
  stat_lineribbon(.width = c(.85, .95), alpha = 1/4) +
  stat_lineribbon(.width = 0, alpha = 0.7) +
  scale_color_brewer(palette = "Set1", name = "") +
  scale_fill_brewer(palette = "Set1", name = "Temperature") + 
  theme_light(base_size = 12) +
  geom_point(data = dat, aes(log_mass_ct, log_y), inherit.aes = FALSE,
             size = 1.5, alpha = 0.6, shape = 21, color = "white", fill = "grey30") + 
  guides(color = "none") +
  labs(x = "log(mass)") + 
  theme(legend.key.size = unit(0.5, "line"), 
        legend.spacing.x = unit(0.1, 'cm'),
        legend.margin = margin(0, 0, 0, 0),
        legend.position = "bottom",
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = unit(c(0, 0.1, 0.5, 0), "cm"))

p2 <- data.frame(
  expand.grid(log_mass_ct = round(c(2, 5) - mean(dat$log_mass), 2), # summary(dat$log_mass)
              temp_arr_ct = seq_range(dat$temp_arr_ct, n = 101))) %>% 
  mutate(log_mass = round(log_mass_ct + mean(dat$log_mass), 2)) %>% 
  add_predicted_draws(m_skew, re_formula = NA) %>%
  ggplot(., aes(x = temp_arr_ct, y = .prediction,
                color = factor(log_mass), fill = factor(log_mass))) +
  stat_lineribbon(.width = c(.85, .95), alpha = 1/4) +
  stat_lineribbon(.width = 0, alpha = 0.7) +
  scale_color_brewer(palette = "Dark2", name = "") +
  scale_fill_brewer(palette = "Dark2", name = "log(mass)") + # Check this! Not the centered scale
  theme_light(base_size = 12) +
  geom_point(data = dat, aes(temp_arr_ct, log_y), inherit.aes = FALSE,
             size = 1.5, alpha = 0.6, shape = 21, color = "white", fill = "grey30") + 
  guides(color = "none") +
  labs(x = "Temperature (1/kT[K])") + 
  theme(legend.key.size = unit(0.5, "line"), 
        legend.spacing.x = unit(0.1, 'cm'),
        legend.margin = margin(0, 0, 1, 0),
        legend.position = "bottom",
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = unit(c(0, 0, 1, 0), "cm"))


get_variables(m_skew)

prop_b3 <- m_skew %>%
  spread_draws(`b_log_mass_ct:temp_arr_ct`) %>% 
  summarise(Proportion_below_0 = sum(`b_log_mass_ct:temp_arr_ct` < 0) / length(`b_log_mass_ct:temp_arr_ct`))

p3 <- m_skew %>%
  spread_draws(`b_log_mass_ct:temp_arr_ct`) %>%
  ggplot(aes(x = `b_log_mass_ct:temp_arr_ct`, fill = stat(x < 0))) +
  stat_halfeye(.width = c(0.85, 0.95)) + 
  theme_light(base_size = 12) + 
  geom_vline(xintercept = 0, linetype = "dashed") +
  scale_fill_manual(values = c("gray90", "grey60")) +
  labs(x = "Mass×Temp. interaction") +
  annotate("text", 0.05, 0.95, size = 3, label = paste("prop. diff<0=", round(prop_b3, 3), sep = "")) +
  theme(legend.key.size = unit(0.5, "line"), 
        legend.spacing.x = unit(0.1, 'cm'),
        legend.margin = margin(0, 0, 0, 0),
        legend.position = "bottom",
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "cm"))
p3

# Compare with and without interaction
df_comp <- data.frame(expand.grid(
  mass = seq(0, 1000, 1),
  temp_arr_ct = seq(min(dat$temp_arr_ct),
                    max(dat$temp_arr_ct),
                    length.out = 20))) %>% 
  mutate(temp_arr = temp_arr_ct + mean(dat$temp_arr),
         temp_c = 1/(temp_arr * (8.617*10^-5)) - 273.15,
         log_mass = log(mass),
         log_mass_ct = log_mass + mean(dat$log_mass),
         temp_c_r = round(temp_c, digits = 0))

intercept <- as.data.frame(fixef(m_skew))$Estimate[1]
mass_coef <- as.data.frame(fixef(m_skew))$Estimate[2]
temp_coef <- as.data.frame(fixef(m_skew))$Estimate[3]
mt_interaction <- as.data.frame(fixef(m_skew))$Estimate[4]

df_comp <- df_comp %>% 
  mutate(log_growth = intercept +
           log_mass_ct*mass_coef +
           temp_arr_ct*temp_coef +
           log_mass_ct*temp_arr_ct*mt_interaction,
         log_growth_no_inter = intercept + log_mass_ct*mass_coef + temp_arr_ct*temp_coef)

# Plot difference in %
unique(df_comp$mass)

p4 <- df_comp %>% 
  filter(mass %in% c(10, 1000) & temp_c_r > 10 & temp_c_r < 25) %>% 
  mutate(growth_percent = 100 * ((exp(log_growth) - exp(log_growth_no_inter)) / exp(log_growth_no_inter)),
         growth_ratio = (exp(log_growth) / exp(log_growth_no_inter)),
         log_growth_percent = 100 * ((log_growth - log_growth_no_inter) / log_growth_no_inter),
         log_growth_ratio = (log_growth / log_growth_no_inter),
         ) %>% 
  ggplot(aes(temp_c_r, growth_ratio, color = factor(mass))) +
  labs(y = "ratio: growth/(growth fixed exponent)",
       x = "Temperature [°C]",
       color = "Mass [g]") +
  scale_color_brewer(palette = "Dark2") +
  geom_line(size = 1.1) + 
  theme_light(base_size = 12) +
  theme(legend.key.size = unit(0.5, "line"), 
        legend.spacing.x = unit(0.1, 'cm'),
        legend.margin = margin(0, 0, 0, 0),
        legend.position = "bottom",
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "cm"))

p4

((p1 + p2) / (p3 + p4)) + plot_annotation(tag_levels = "A")
ggsave("figures/Fig1.png", width = 6.5, height = 6.5, dpi = 600)

# Fix margins, calculate area under curve and add to plot

get_variables(m_skew)

p5 <- m_skew %>%
  spread_draws(b_Intercept, r_species_ab[species_ab, ]) %>%
  mutate(intercept_mean = b_Intercept + r_species_ab) %>%
  ggplot(aes(y = species_ab, x = intercept_mean)) +
  stat_halfeye(size = 0.5) + 
  theme_light(base_size = 12) + 
  scale_fill_manual(values = c("gray80", "tomato")) + 
  theme(legend.position = "bottom", 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text.y = element_text(face = "italic")) + 
  labs(y = "Species", x = "Intercept") +
  NULL

p5
ggsave("figures/Fig2.png", width = 3, height = 4, dpi = 600)
```

## Supporting figures

```{r plot model validation}
# Plot model diagnostics
# Model validation
posterior <- as.array(m_skew)
dimnames(posterior)

mcmc_trace(
  posterior, 
  pars = c("b_Intercept", "b_log_mass_ct", 
           "b_temp_arr_ct", "b_log_mass_ct:temp_arr_ct", "sd_species_ab__Intercept",
           "sd_species_ab__Intercept", "sigma", "alpha"),
  facet_args = list(ncol = 2, strip.position = "left")) + 
  geom_line(alpha = .2) +
  theme(text = element_text(size = 12),
        strip.text = element_text(size = 3),
        legend.position = c(0.6, 0.05),
        legend.direction = "horizontal") + 
  scale_color_viridis(discrete = TRUE, direction = -1) +
  theme_light(base_size = 12) +
  theme(axis.text.x = element_text(angle = 90),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = c(0.75, 0.1),
        strip.text = element_text(size = 5, colour = 'gray10', margin = margin(b = 1, t = 1)),
        strip.background = element_rect(fill = "grey95"),
        legend.direction = "horizontal") + 
  NULL

ggsave("figures/FigS1.png", width = 6.5, height = 6.5, dpi = 600)

# Posterior predictive
pp_check(m_skew) + 
  theme(text = element_text(size = 12),
        legend.position = c(0.15, 0.95),
        legend.background = element_rect(fill = NA)) + 
  scale_color_brewer(palette = "Dark2") +
  labs(color = "") +
  theme_light(base_size = 9) +
  theme(legend.position = c(0.2, 0.8),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) + 
  NULL

ggsave("figures/FigS2.png", width = 3.5, height = 3.5, dpi = 600)
```

```{r}
# Sensitivity analysis
coef_list <- list()

for(i in unique(dat$species_ab)) {
  
  dat2 <- dat %>% filter(!species_ab == i)
  
  m <- brm(
  log_y ~ log_mass_ct*temp_arr_ct + (1 | species_ab),
  data = filter(dat2, above_peak_temp == "N"),
  family = skew_normal(),
  save_pars = save_pars(all = TRUE),
  control = list(adapt_delta = 0.95, max_treedepth = 12),
  iter = 4000, cores = 4, chains = 4)

  coef <- fixef(m) %>% 
    as.data.frame() %>% 
    tibble::rownames_to_column("par") %>% 
    mutate(Species = i)
  
  coef_list[[i]] <- coef
    
}

coefs <- bind_rows(coef_list)

ggplot(coefs, aes(Estimate, Species, xmin = Q2.5, xmax = Q97.5)) + 
  geom_pointrange() +
  facet_wrap(~par, scales = "free") + 
  theme_light(base_size = 12) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  NULL
  
# Sensitivity analysis
coefs$par

coefs <- coefs %>% 
  mutate(par2 = ifelse(par == "log_mass_ct", "Mass-coefficient", par),
         par2 = ifelse(par == "temp_arr_ct", "Temperature-coefficient", par2),
         par2 = ifelse(par == "log_mass_ct:temp_arr_ct", "Mass-temperature interaction", par2))

coef_main <- fixef(m_skew) %>% 
  as.data.frame() %>% 
  tibble::rownames_to_column("par") %>% 
  mutate(par2 = ifelse(par == "log_mass_ct", "Mass-coefficient", par),
         par2 = ifelse(par == "temp_arr_ct", "Temperature-coefficient", par2),
         par2 = ifelse(par == "log_mass_ct:temp_arr_ct", "Mass-temperature interaction", par2)) %>% 
  filter(!par %in% c("Intercept"))

coefs %>% 
  filter(!par %in% c("Intercept")) %>% 
  ggplot(aes(Estimate, Species, xmin = Q2.5, xmax = Q97.5)) + 
  geom_vline(data = coefs %>% filter(par2 == "Mass-temperature interaction"),
             aes(xintercept = 0), col = "tomato2", linetype = 2, size = 0.8) +
  geom_vline(data = coef_main, aes(xintercept = Estimate), alpha = 0.5) +
  geom_pointrange(size = 0.2) +
  facet_wrap(~par2, scales = "free", ncol = 1) + 
  theme_light(base_size = 12) +
  theme(legend.position = c(0.2, 0.9),
        axis.text.y = element_text(face = "italic"), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.text = element_text(colour = 'gray10', margin = margin(b = 1, t = 1)),
        strip.background = element_rect(fill = "grey95")) +
  NULL

ggsave("figures/FigS3.png", width = 6, height = 6, dpi = 600)
```